### 2019-09-13 upper.tex
general online for k=3

\begin{theorem}
  The rebalancing cost for the greedy algorithm for $k=3$ is $O(1)$.
  \maciek{Greedy = find the cheapest (closest to the current) feasible partition}
  \label{rebalancing-cost}
\end{theorem}

@@

\begin{theorem}
  There exists a $O(\ell)$-competitive algorithm for $k=3$.
\end{theorem}

\begin{proof}
  The adversary issues at most $3\ell$ requests, as otherwise the perfect partition would not exist. Each request issues at most one rebalancingfor the greedy algorithm, and by Theorem~\ref{rebalancing-cost}, the total cost of any algorithm is $O(k\cdot \ell)$.
\end{proof}

>>>>

\begin{lemma} \label{lemma:k=3}
  The rebalancing cost for the greedy algorithm for $k=3$ is $O(1)$.
  \maciek{Greedy = find the cheapest (closest to the current) feasible partition}
  \label{rebalancing-cost}
\end{lemma}

@@

\begin{theorem}
  There exists a $O(\ell)$-competitive algorithm for $k=3$.
\mahmoud{is this needed anymore?}
\end{theorem}

\begin{proof}
  The adversary issues at most $3\ell$ requests, as otherwise the perfect partition would not exist. Each request issues at most one re-balancing for the greedy algorithm, and by Theorem~\ref{rebalancing-cost}, the total cost of any algorithm is $O(k\cdot \ell)$.
\end{proof}

We leverage the simple algorithm $ON_{k=3}$ that seeks a perfect partition for $k=3$ towards an algorithm for the general online problem.
Note that in the general model, an optimal partition is not a necessarily a perfect partition.
We divide the sequence of requests into phases.
A phase terminates when there is no perfect partition of components after arrival of some request $r$.
We apply requests to $ON_{k=3}$ as before. 
Once the current phase terminates,
we reset all components by removing (forgetting) all revealed edges,
 and then we proceed to the next phase.

\begin{corollary} \label{cor:k=3}
	There exists $O(\ell)$-competitive  algorithm for the general online problem when $k=3$. 
\end{corollary}
\begin{proof}
	Consider any phase and assume it terminates upon arrival of some request $r$.
	 By Lemma  \ref{lemma:k=3},
	ON pays $O(\ell)$ during the phase.
	Regardless of the of OPT's partition at the beginning of the phase,
	as long as OPT stays in the same configuration,
	 it incurs remote communication cost for at least one request $r'$ (possibly $r'=r$) by the end of the phase.
	 Else,
	 OPT incurs the cost of moving to new partitions.
	 In any case,
	 OPT must pay at least one during the phase.
\end{proof}
